Are rankings of financial analysts useful to investors?

### 2015-03-17 doc/paper/paper-knitr-APS.Rnw
paper with table side-by-side all and same set of stocks

\documentclass{article}
\usepackage{fancyhdr}
\usepackage{time}
\usepackage{authblk}
\usepackage{amsmath, amssymb}
\usepackage{caption}
\captionsetup[table]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
\captionsetup[figure]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
%\usepackage{fullpage}
%\usepackage{rotating}
%\usepackage{xcolor}
\usepackage[hyphens]{url}
\usepackage[colorlinks=true,urlcolor=blue,citecolor=black]{hyperref}
%\usepackage{breakurl}
\usepackage{times}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{array}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{adjustbox}
%\onehalfspacing
\doublespace
\usepackage[longnamesfirst]{natbib}
%\usepackage[natbibapa,longnamesfist]{apacite}

@@

\begin{tabularx}{\linewidth}{r*{4}{Y}}
\toprule
& Mean (in \%) & Median (in \%) &Std.dev\\
\midrule
<<desc-q-cons,echo=F,results='asis'>>=
test.a[,,,1:2,'all'] <- test.a[,,,1:2,'all']*100
dimnames(test.a)[[2]] <- c('\\tr{}','\\naive{}','\\default{}')
print(xtable(aperm(test.a[12,,,1:3,'all'],c(1,3,2))[,,1],display=c('s','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{4}{l}{\\textbf{Panel A: Consensus}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
@
\end{tabularx}

  \begin{tabularx}{\linewidth}{r*{4}{Y}}
  \midrule
<<desc-q-naive,echo=F,results='asis'>>=
#data.to.display <- c('nbr.val','mean', 'median','std.dev')

#cat(rep('&',ncol(results.final)),'\\\\')
print(xtable(aperm(test.a[12,,,1:3,'all'],c(1,3,2))[,,2],display=c('s','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{4}{l}{\\textbf{Panel B: TP}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
@
  \end{tabularx}
  \begin{tabularx}{\linewidth}{r*{4}{Y}}
<<desc-q-eps,echo=F,results='asis'>>=
#data.to.display <- c('nbr.val','mean', 'median','std.dev')

#cat(rep('&',ncol(results.final)),'\\\\')
print(xtable(aperm(test.a[12,,,1:3,'all'],c(1,3,2))[,,3],display=c('s','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{4}{l}{\\textbf{Panel C: EPS}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
@
\bottomrule
\end{tabularx}
  \end{table}

\begin{table}[hp]
  \caption{Number of active stocks}
  \label{tab:stocks}
\ This table shows number of active stocks in each of the trading strategies conditional on different information sets: \tr{} (panel A), \naive{} (panel B) and \default{} (panel C). 
\begin{tabularx}{\linewidth}{r*{4}{Y}}
\toprule
Year& \textit{CONS}& \textit{TP} & \textit{EPS}\\
<<stocks-true,echo=F,results='asis'>>=
print(xtable(aperm(test.a[,,c(1,3,2),4,'all'],c(1,3,2))[,,1],display=c('s','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{4}{l}{\\textbf{Panel A: \\tr{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
@
\end{tabularx}
\begin{tabularx}{\linewidth}{r*{4}{Y}}
<<stocks-naive,echo=F,results='asis'>>=
print(xtable(aperm(test.a[,,c(1,3,2),4,'all'],c(1,3,2))[,,2],display=c('s','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{4}{l}{\\textbf{Panel B: \\naive{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
@
\end{tabularx}
\begin{tabularx}{\linewidth}{r*{4}{Y}}
<<stocks-def,echo=F,results='asis'>>=
print(xtable(aperm(test.a[,,c(1,3,2),4,'all'],c(1,3,2))[,,3],display=c('s','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{4}{l}{\\textbf{Panel C: \\default{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
@
\bottomrule
\end{tabularx}
\end{table}

%'   \begin{table}[hp]
%'   \caption{Descriptive statistics of views: \tr{}}
%'   \label{tab:view-stat}
%'   \small\addtolength{\tabcolsep}{-2pt}
%'   
%' \ This table shows the descriptive (per stock per quarter) statistics of views (expected returns) for the \tr{} (\ref{q:true}) based on the consensus (median) among the analysts (panel A); target price rankings (panel B); and EPS forecasts rankings (panel C).
%'   
%' \begin{tabularx}{\linewidth}{r*{5}{Y}}
%'     \toprule
%' Year &Stocks& Mean & Median &Std.dev\\
%' \midrule
%' <<desc-nr.views,echo=F,results='asis'>>=
%' 
%' print(xtable(test.a[,1,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{consq})}} \\\\','\\midrule \n')))
%' @
%'   \midrule
%'   \end{tabularx}
%' 
%'   \begin{tabularx}{\linewidth}{r*{5}{Y}}
%'   \midrule
%' <<desc-r.views,echo=F,results='asis'>>=
%' #data.to.display <- c('nbr.val','mean', 'median','std.dev')
%' 
%' #cat(rep('&',ncol(results.final)),'\\\\')
%' print(xtable(test.a[,1,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{rankq})}} \\\\','\\midrule \n','\\midrule \n')))
%' @
%'   \end{tabularx}
%'   
%' 
%'   \begin{tabularx}{\linewidth}{r*{5}{Y}}
%'   \midrule
%' <<desc-eps.views,echo=F,results='asis'>>=
%' #data.to.display <- c('nbr.val','mean', 'median','std.dev')
%' 
%' print(xtable(test.a[,1,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{rankq})}} \\\\','\\midrule \n')))
%' @
%' \bottomrule
%'   \end{tabularx}
%' \end{table}
%' 
%' 
%' \begin{table}[hp]
%'   \caption{Descriptive statistics of views: \naive{}}
%'   \label{tab:view-stat-naive}
%'   \small\addtolength{\tabcolsep}{-2pt}
%'   
%' \ This table shows descriptive statistics of views (expected returns) for the \naive{} (\ref{q:naive}) based on: the consensus among the analysts (panel A), target price rankings (panel B), and EPS forecasts rankings (panel C) per stock per quarter.
%'   
%' \begin{tabularx}{\linewidth}{r*{5}{Y}}
%'     \toprule
%' Year &Stocks& Mean & Median &Std.dev\\
%' \midrule
%' <<desc-nr.views-naive,echo=F,results='asis'>>=
%' 
%' print(xtable(test.a[,2,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{consq})}} \\\\','\\midrule \n')))
%' @
%'   \midrule
%'   \end{tabularx}
%' 
%'   \begin{tabularx}{\linewidth}{r*{5}{Y}}
%'   \midrule
%' <<desc-r.views-naive,echo=F,results='asis'>>=
%' #data.to.display <- c('nbr.val','mean', 'median','std.dev')
%' 
%' #cat(rep('&',ncol(results.final)),'\\\\')
%' print(xtable(test.a[,2,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{rankq})}} \\\\','\\midrule \n','\\midrule \n')))
%' @
%'   \end{tabularx}
%' 
%'   \begin{tabularx}{\linewidth}{r*{5}{Y}}
%'   \midrule
%' <<desc-eps.views-naive,echo=F,results='asis'>>=
%' #data.to.display <- c('nbr.val','mean', 'median','std.dev')
%' 
%' print(xtable(test.a[,2,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{rankq})}} \\\\','\\midrule \n')))
%' @
%' \bottomrule
%'   \end{tabularx}
%' \end{table}
%' 
%' \begin{table}[hp]
%'   \caption{Descriptive statistics of views: \default{}}
%'   \label{tab:view-stat-default}
%'   \small\addtolength{\tabcolsep}{-2pt}
%'   
%' \ This table shows descriptive statistics of views (expected returns) for the \default{} (\ref{q:default}) based on: the consensus among the analysts (panel A), target price rankings (panel B), and EPS forecasts rankings (panel C) per stock per quarter.
%'   
%' \begin{tabularx}{\linewidth}{r*{5}{Y}}
%'     \toprule
%' Year &Stocks& Mean & Median &Std.dev\\
%' \midrule
%' <<desc-nr.views-default,echo=F,results='asis'>>=
%' 
%' print(xtable(test.a[,3,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{consq})}} \\\\','\\midrule \n','\\midrule \n')))
%' @
%'   \midrule
%'   \end{tabularx}
%' 
%'   \begin{tabularx}{\linewidth}{r*{5}{Y}}
%'   \midrule
%' <<desc-r.views-default,echo=F,results='asis'>>=
%' #data.to.display <- c('nbr.val','mean', 'median','std.dev')
%' 
%' #cat(rep('&',ncol(results.final)),'\\\\')
%' print(xtable(test.a[,3,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{rankq})}} \\\\','\\midrule \n','\\midrule \n')))
%' @
%'   \end{tabularx}
%' 
%'   \begin{tabularx}{\linewidth}{r*{5}{Y}}
%'   \midrule
%' <<desc-eps.views-default,echo=F,results='asis'>>=
%' #data.to.display <- c('nbr.val','mean', 'median','std.dev')
%' 
%' print(xtable(test.a[,3,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{rankq})}} \\\\','\\midrule \n')))
%' @
%' \bottomrule
%'   \end{tabularx}
%' \end{table}

@@

#p.cum.ret <-
ggplot(final.bl,aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views,shape=Views))+geom_line(size=0.5)+facet_grid(type~Method,scale='free_x')+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw()+theme(plot.title = element_text(colour = "Black"),legend.position='top',legend.title=element_blank(),strip.text=element_text(size=20),text=element_text(size=20,family='Times'))+scale_color_grey()+geom_point()+geom_hline(yintercept=100)
#+scale_color_manual(values=getPalette(colourCount))+guides(color=guide_legend(nrow=1))

#+scale_color_manual(values=getPalette(colourCount))+

#+scale_x_date(breaks='year',labels=date_format('%Y'))

#p.ann.ret <-ggplot(unique(melt(final.bl[Aggregation=='ma',list(Views,Method,ann.ret,ann.sd,ann.sr)],id.vars=c('Method','Views'))),aes(x=Views,y=value))+geom_bar(aes(fill=Views),stat='identity',alpha=0.7)+facet_grid(variable~Method,scale='free_y')+theme_bw()+ggtitle('Annualized portfolio measures (return, st.dev, and the Sharpe ratio) \n conditional on confidence aggregation')+theme(plot.title = element_text(colour = "Blue"),legend.position='top',axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+scale_y_continuous(labels=percent)+ylab('Percent')+geom_text(aes(label=round(value,3)*100),angle=90,size=3,hjust=1.2)+scale_fill_manual(values=getPalette(colourCount))

#p.TO <-ggplot(unique(melt(final.bl[Aggregation=='ma',list(Views,Method,meanViews,Ave.TO)],id.vars=c('Method','Views'))),aes(x=Views,y=value,fill=Views))+theme_bw()+geom_bar(stat='identity')+facet_grid(variable~Method,scale='free_y')+ggtitle('Trading statistics conditional confidence aggregation \n (averages of number of views and turnover ratio)')+theme(legend.position='none',axis.title.x=element_blank(),plot.title = element_text(colour = "Blue"),axis.title.y=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+scale_fill_manual(values=getPalette(colourCount))

#grid.arrange(p.cum.ret,p.ann.ret,rectGrob(gp=gpar(lwd=2, fill=NA)))
#grid.draw(grobTree(arrangeGrob(p.cum.ret,ncol=1),rectGrob(gp=gpar(lwd=2, fill=NA))))
@

@@

dimnames(bl.results)[[1]] <- c('\\textit{CONS}','\\textit{TP}','\\textit{EPS}','\\textit{Market}')
results.final <- bl.results[4,1,,'all']
cat(paste(c('Strategy','Annualized return (in \\%)','Annualized Std. dev (in \\%)','Sharpe ratio' ,'Average num. stock','Average turnover rate'), collapse = "&"),'\\\\')
#cat('\\multicolumn{5}{l}{\\textbf{Panel A: Market}} \n')
print(xtable(t(data.table('\\textit{Market}'=results.final)),display=c('s','f','f','f','d','f'),digits=4,align=c('r',rep('c',length(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel A}} \\\\ \n')),sanitize.text.function = function(x) x)
cat('\\midrule \n')
@
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel B: \tr{} }} \\
<<bl-nr,echo=F,results='asis'>>=
print(xtable(bl.results[1:3,1,,'all'],display=c('s','f','f','f','d','f'),digits=4),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(bl.results[1:3,1,,'all'])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
@
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel C: \naive{}}} \\
<<bl-pt,echo=F,results='asis'>>=
print(xtable(bl.results[1:3,2,,'all'],display=c('s','f','f','f','d','f'),digits=4),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),,add.to.row=list(pos=list(nrow(bl.results[1:3,2,,'all'])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
@
\end{tabularx}
\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel D: \default{}}} \\
<<bl-eps,echo=F,results='asis'>>=
print(xtable(bl.results[1:3,3,,'all'],display=c('s','f','f','f','d','f'),digits=4),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),sanitize.text.function = function(x) x)
@
\bottomrule
\end{tabularx}
\end{table}

@@

print(xtable(acast(melt(periods.array[,c(4,1,2,3),1,'yes',c(1,4),'all']),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=4),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel A: \\tr{}}} \\\\\n', '\\midrule \n')))

@@

print(xtable(acast(melt(periods.array[,c(4,1,2,3),2,'yes',c(1,4),'all']),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=4),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel B: \\naive{}}} \\\\\n', '\\midrule \n')))

@@

print(xtable(acast(melt(periods.array[,c(4,1,2,3),3,'yes',c(1,4),'all']),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=4),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{5}{l}{\\textbf{Panel C: \\default{}}} \\\\\n','\\midrule \n')))
@
\bottomrule
\end{tabular}}
\end{table}

>>>>

\documentclass{article}
\usepackage{fancyhdr}
\usepackage{time}
\usepackage{authblk}
\usepackage{amsmath, amssymb}
\usepackage{caption}
\captionsetup[table]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
\captionsetup[figure]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
%\usepackage{fullpage}
%\usepackage{rotating}
%\usepackage{xcolor}
\usepackage[hyphens]{url}
\usepackage[colorlinks=true,urlcolor=blue,citecolor=black]{hyperref}
%\usepackage{breakurl}
\usepackage{times}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{array}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{adjustbox}
%\usepackage{floatpag}
%\onehalfspacing
\doublespace
\usepackage[longnamesfirst]{natbib}
%\usepackage[natbibapa,longnamesfist]{apacite}

@@

\begin{tabularx}{\linewidth}{r*{7}{Y}}
\toprule
& \multicolumn{2}{c}{Mean (in \%)}&\multicolumn{2}{c}{Median (in \%)}& \multicolumn{2}{c}{Std.dev}\\
&all&same&all&same&all&same\\
\midrule
<<desc-q-cons,echo=F,results='asis'>>=
test.a[,,,1:2,] <- test.a[,,,1:2,]*100
dimnames(test.a)[[2]] <- c('\\tr{}','\\naive{}','\\default{}')
print(xtable(acast(melt(test.a[12,,'CONS',1:3,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{7}{c}{\\textbf{Panel A: Consensus}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
@
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{7}{Y}}
  \midrule
<<desc-q-naive,echo=F,results='asis'>>=
#data.to.display <- c('nbr.val','mean', 'median','std.dev')

#cat(rep('&',ncol(results.final)),'\\\\')
print(xtable(acast(melt(test.a[12,,'PT',1:3,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{7}{c}{\\textbf{Panel B: TP}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
@
  \end{tabularx}

\begin{tabularx}{\linewidth}{r*{7}{Y}}
<<desc-q-eps,echo=F,results='asis'>>=
print(xtable(acast(melt(test.a[12,,'EPS',1:3,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{7}{c}{\\textbf{Panel C: EPS}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
@
\bottomrule
\end{tabularx}
  \end{table}

\begin{table}[hp]
  \caption{Number of active stocks}
  \label{tab:stocks}
\ This table shows number of active stocks in each of the trading strategies conditional on different information sets: \tr{} (panel A), \naive{} (panel B) and \default{} (panel C).

%\resizebox{\textwidth}{!}{%
%\begin{tabular}{rrrrrrr}
\begin{tabularx}{\linewidth}{r*{7}{Y}}
\toprule
Year&\multicolumn{2}{c}{\textit{CONS}}& \multicolumn{2}{c}{\textit{TP}} &\multicolumn{2}{c}{\textit{EPS}}\\
&all&same&all&same&all&same\\
<<stocks-true,echo=F,results='asis'>>=
print(xtable(acast(melt(test.a[,1,c(1,3,2),4,]),Var1~Var2+Var3,value.var='value'),display=c('s','d','d','d','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{7}{l}{\\textbf{Panel A: \\tr{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
@
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{7}{Y}}
<<stocks-naive,echo=F,results='asis'>>=
print(xtable(acast(melt(test.a[,2,c(1,3,2),4,]),Var1~Var2+Var3,value.var='value'),display=c('s','d','d','d','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{7}{l}{\\textbf{Panel B: \\naive{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
@
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{7}{Y}}
<<stocks-def,echo=F,results='asis'>>=
print(xtable(acast(melt(test.a[,3,c(1,3,2),4,]),Var1~Var2+Var3,value.var='value'),display=c('s','d','d','d','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{7}{l}{\\textbf{Panel C: \\default{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
@
\bottomrule
\end{tabularx}
\end{table}

@@

#p.cum.ret <-
ggplot(final.bl,aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views,shape=Views))+geom_line(size=0.5)+facet_grid(type~Method,scale='free_x')+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw()+theme(plot.title = element_text(colour = "Black"),legend.position='top',legend.title=element_blank(),strip.text=element_text(size=20),text=element_text(size=20,family='Times'))+scale_color_grey()+geom_point()+geom_hline(yintercept=100)
#
@

@@

dimnames(bl.results)[[1]] <- c('\\textit{CONS}','\\textit{TP}','\\textit{EPS}','\\textit{Market}')
results.final <- bl.results[4,1,,'all']
cat(paste(c('Strategy','Annualized return (in \\%)','Annualized Std. dev (in \\%)','Sharpe ratio' ,'Average num. stock','Average turnover rate'), collapse = "&"),'\\\\')
#cat('\\multicolumn{5}{l}{\\textbf{Panel A: Market}} \n')
print(xtable(t(data.table('\\textit{Market}'=results.final)),display=c('s','f','f','f','d','f'),digits=3,align=c('r',rep('c',length(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel A}} \\\\ \n')),sanitize.text.function = function(x) x)
cat('\\midrule \n')
@
\end{tabularx}

\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrrrr}
  \multicolumn{11}{c}{\textbf{Panel B: \tr{} }} \\
  &all&same&all&same&all&same&all&same&all&same \\

<<bl-nr,echo=F,results='asis'>>=
print(xtable(acast(melt(bl.results[1:3,1,,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','d','d','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(bl.results[1:3,1,,'all'])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
@
\end{tabular}}

\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrrrr}
  \multicolumn{11}{c}{\textbf{Panel C: \naive{}}} \\
<<bl-pt,echo=F,results='asis'>>=
print(xtable(acast(melt(bl.results[1:3,2,,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','d','d','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),,add.to.row=list(pos=list(nrow(bl.results[1:3,2,,'all'])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
@
\end{tabular}}

\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrrrr}
  \multicolumn{11}{c}{\textbf{Panel D: \default{}}} \\
<<bl-eps,echo=F,results='asis'>>=
print(xtable(acast(melt(bl.results[1:3,3,,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','d','d','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),sanitize.text.function = function(x) x)
@
\bottomrule
\end{tabular}}
\end{table}

@@

print(xtable(acast(melt(periods.array[,c(4,1,2,3),1,'yes',c(1,4),'all']),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel A: \\tr{}}} \\\\\n', '\\midrule \n')))

@@

print(xtable(acast(melt(periods.array[,c(4,1,2,3),2,'yes',c(1,4),'all']),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel B: \\naive{}}} \\\\\n', '\\midrule \n')))

@@

print(xtable(acast(melt(periods.array[,c(4,1,2,3),3,'yes',c(1,4),'all']),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{5}{l}{\\textbf{Panel C: \\default{}}} \\\\\n','\\midrule \n')))
@
\bottomrule
\end{tabular}}
\end{table}
